GVN-Hoist: Hoisting Computations from Branches

### 2016-08-05 hoist.tex
some introduction

  Code hoisting is often confused with CSE (Common Subexpression Elimination)
  although hoisting is not bound to find redundancies within a single basic
  block.  Code hoisting could also be confused with Partial Redundancy
  Elimination (PRE) or even with Global Common Subexpression Elimination (GCSE)
  although the main goal of code hoisting is not to remove redundancies: code
  hoisting effectively exposes redundancies and enables other passes like LICM
  to remove more redundancies.  The main goal of code hoisting is to reduce code
  size with the added benefit of exposing instruction level parallelism and
  reduced register pressure.
\end{abstract}

@@

>>>>

  Code hoisting is often confused with CSE (Common Subexpression Elimination)
  although hoisting is not bound to find redundancies within a single basic
  block.  Code hoisting could also be confused with Partial Redundancy
  Elimination (PRE) or even with Global Common Subexpression Elimination (GCSE)
  although the main goal of code hoisting is not to remove redundancies: code
  hoisting effectively exposes redundancies and enables other passes like LICM
  to remove more redundancies.  The main goal of code hoisting is to reduce code
  size with the added benefit of exposing more instruction level parallelism and
  reduced register pressure.
\end{abstract}

@@

Classical scalar optimizations like CSE \cite{dragonbook} work very well on
single basic blocks.  With time, we have seen the transition to more complex
passes like GCSE that work across basic blocks, or other passes like the
macroblock formation that create a region within
